Powdery Milder yield loss mitigation strategies in Mungbean a Meta-analysis

### 2019-09-01 04_Prep_data.Rmd
Correction to code typo

# caluculate yield gain and prop_yield gain for experiments with no row spacing data
dat1 <- PM_MB_means[PM_MB_means$Trial_ref == "AM1303",]
controlY <- mean(dat2[dat1$Fungicide == "control","grain_yield.t.ha."])
dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
dat1$prop_YG <- dat1$yield_gain/controlY
dat1[dat1$Fungicide == "control",c("yield_gain", "prop_YG")] <- NA
PM_MB_means[PM_MB_means$Trial_ref == "AM1303",] <- dat1

>>>>

# caluculate yield gain and prop_yield gain for experiments with no row spacing data
dat1 <- PM_MB_means[PM_MB_means$Trial_ref == "AM1303",]
controlY <- mean(dat1[dat1$Fungicide == "control","grain_yield.t.ha."])
dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
dat1$prop_YG <- dat1$yield_gain/controlY
dat1[dat1$Fungicide == "control",c("yield_gain", "prop_YG")] <- NA
PM_MB_means[PM_MB_means$Trial_ref == "AM1303",] <- dat1
